method

### 2021-09-21 06_Paper/ER-ED/method.Rmd
added sections
added text

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
Each possible pairing of strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) was presented in a randomized order.
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

@@

>>>>

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013]
For each possible pairing, two strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) with monetary values were presented.
The order of the comparisons was randomized.

Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

@@

## 2.5 Electromyography

## 2.6 Psychometric measures

## 2.7 Statistics
